UZH IT \& AI Emissions Analysis\vspace{-1em}

### 2024-12-03 doc.tex
Update power estimates.

\addbibresource{ref.bib}
\title{UZH IT \& AI Emissions Analysis\vspace{-1em}}
\author{Massimiliano Poletto}
\date{\vspace{-1em}29.11.2024}

@@

\begin{center}
\begin{tabular}{|l|r|r|}
\hline
\textbf{Device} & \textbf{Mean (W)} & \textbf{$\sigma$ (W)} \\ \hline
Laptop & 30 & 5 \\ \hline
Desktop & 100 & 20 \\ \hline
Server & 400 & 100 \\ \hline
Phone & 5 & 2 \\ \hline
Monitor & 50 & 10 \\ \hline
Conference display & 120 & 25 \\ \hline
Printer/copier & 1000 & 200 \\ \hline
\end{tabular}
\end{center}

>>>>

\addbibresource{ref.bib}
\title{UZH IT \& AI Emissions Analysis\vspace{-1em}}
\author{Massimiliano Poletto}
\date{\vspace{-1em}29.11.2024\footnote{Last modified: \today}}

@@

\begin{center}
\begin{tabular}{|l|r|r|}
\hline
\textbf{Device} & \textbf{Mean (W)} & \textbf{$\sigma$ (W)} \\ \hline
Laptop & 30 & 5 \\ \hline
Desktop & 100 & 20 \\ \hline
Server & 400 & 100 \\ \hline
Phone & 5 & 2 \\ \hline
Monitor & 50 & 10 \\ \hline
Conference display & 250 & 50 \\ \hline
Printer/copier & 1000 & 200 \\ \hline
\end{tabular}
\end{center}
